### 2015-12-11 paper/4-performance.tex
Update changed call graphs adevs interconnect. Proxy commit R script and new graphs and try to fit them in paper.

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/queue_sequential.eps}
	\caption{Queue benchmark results for sequential simulation.}
	\label{fig:Queue_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/interconnect_sequential.eps}
	\caption{Interconnect benchmark results for sequential simulation.}
	\label{fig:Interconnect_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/queue_parallel.eps}
	\caption{Queue benchmark results for parallel simulation of a model of fixed size.}
	\label{fig:queue_benchmark_parallel}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_voorlopig.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
    \caption{Interconnect benchmark results for parallel simulation.}
    \label{fig:interconnect_benchmark_parallel}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth,height=6cm]{fig/queue_sequential.eps}
	\caption{Queue benchmark results for sequential simulation.}
	\label{fig:Queue_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth,height=6cm]{fig/interconnect_sequential.eps}
	\caption{Interconnect benchmark results for sequential simulation.}
	\label{fig:Interconnect_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth,height=6cm]{fig/queue_parallel.eps}
	\caption{Queue benchmark results for parallel simulation of a model of fixed size.}
	\label{fig:queue_benchmark_parallel}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6cm]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6cm]{fig/phold_priority.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6cm]{fig/interconnect_parallel.eps}
    \caption{Interconnect benchmark results for parallel simulation.}
    \label{fig:interconnect_benchmark_parallel}
\end{figure}
